BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for BPMN Models

### 2024-07-05 main.tex
4 pages

Our tool has comparable BPMN element coverage to~\cite{corradiniFormalApproachAnalysis2021} but is still missing some elements when compared to~\cite{krauterFormalizationAnalysisBPMN2023}, which are currently on the roadmap. 
In addition, we demonstrated the instantaneous analysis of the BPMN Analyzer, which outperforms other tools~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022} as described in \autoref{sec:innovations}.
Finally, we have only received positive feedback regarding the tool's usability.

>>>>

Our tool has comparable BPMN element coverage to~\cite{corradiniFormalApproachAnalysis2021} but is still missing some elements when compared to~\cite{krauterFormalizationAnalysisBPMN2023}, which are currently on the roadmap. 
In addition, we demonstrated the instantaneous analysis of the BPMN Analyzer, which outperforms other tools~\cite{krauterFormalizationAnalysisBPMN2023,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022} as described in \autoref{sec:innovations}.
However, comparing tool performance without standard benchmarks and a reproducible environment remains challenging.
Finally, we have only received positive feedback regarding the tool's usability, especially the interactive visualization of control flow errors.
Our visualization builds on the~\cite{camundaservicesgmbhBpmnjsTokenSimulation2024} and is similar to the animation capabilities in~\cite{corradiniFormalisingAnimatingMultiple2022}.
